Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2019-01-21 paper/manuscript.tex
fixing double citation

In some cases, it is tempting to simply use docking techniques to generate initial bound structures for starting molecular dynamics simulations.
However, timescales for binding mode interconversion are usually slow compared to MD/free energy timescales, meaning that simulations started from different potential binding modes are likely to yield disparate computed binding free energies~\cite{~\cite{Mobley:2006:TheJournalofChemicalPhysics, Palma:2012:J.Comput.Chem., Mobley:2012:TheJournalofChemicalPhysics, Gill:2018:J.Phys.Chem.B} }.
And docking techniques are good at identifying sterically reasonable potential binding modes, but still perform relatively poorly at identifying a single dominant binding mode \emph{a priori}. [refs]

>>>>

In some cases, it is tempting to simply use docking techniques to generate initial bound structures for starting molecular dynamics simulations.
However, timescales for binding mode interconversion are usually slow compared to MD/free energy timescales, meaning that simulations started from different potential binding modes are likely to yield disparate computed binding free energies~\cite{Mobley:2006:TheJournalofChemicalPhysics, Palma:2012:J.Comput.Chem., Mobley:2012:TheJournalofChemicalPhysics, Gill:2018:J.Phys.Chem.B} .
And docking techniques are good at identifying sterically reasonable potential binding modes, but still perform relatively poorly at identifying a single dominant binding mode \emph{a priori}. [refs]
